The Wolf in Sheep's Clothing\\ Subversive Adversarial Agent Identification

### 2016-08-04 article.tex
Update abstract and add other option for conclusion sentence

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Mobile robot security is a rapidly developing area of interest in robotics.As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. This system is implemented on the TurtleBot platform using the Robot Operating System, and performance is also evaluated in the Gazebo simulator.
\end{abstract}

@@

% conference papers do not normally have an appendix

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Mobile robot security is a rapidly developing area of interest in robotics.As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this a state detection system is added that allows agents to detect subversive or malfunctioning agents in their environment. This system is implemented on the TurtleBot platform using the Robot Operating System, and performance is also evaluated in the Gazebo simulator.
\end{abstract}

@@

We have presented a simple distributed state estimation scheme operating over secure network channels that improves the performance of each agent and is augmented with a state detection scheme allowing agents to recognize possible subversive agents in their environment.
% conference papers do not normally have an appendix
